Draft: Notes on the revised Hidden weight function

### 2024-07-31 RevisedHiddenWeight.tex
Added small remark
Updates from Overleaf

We can also use Property \ref{prop:generating_fct} to obtain $\Dnka nka$ through differentiation:
\[
    k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}.
\]
Using this formula, we can for instance use a computer algebra system to deduce $\Dnka nka$ for small values of $k$, see Table \ref{tab:Dnka_small_k}. Note that even though the expression for $\Dnka n3a$ involves a division by $3$, its evaluation at specific values for $(p,q,r)$ will always yield integers. Indeed, either $p-q\equiv 0\bmod 3$, or $(p-q)^2\equiv 1\bmod 3$, in which case $2(p-q)^2+7\equiv 0\bmod 3$.

\begin{table}
	\centering
	\begin{tabular}{|c|c|}
		\hline
		$k$ & $\Dnka nka$\\ \hline
		$0$&$1$\\ \hline
        $1$&$2(p-q)$\\ \hline
        $2$&$2(p-q)^2-3(p+q)+r$\\ \hline
        $3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\ \hline
	\end{tabular}
	\caption{Values of $\Dnka{n}{k}{a}$ for small $k$}\label{tab:Dnka_small_k}
\end{table}

@@

>>>>

\begin{remark}
    We can also use Property \ref{prop:generating_fct} to obtain $\Dnka nka$ through differentiation:
    \[
        k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}.
    \]
    Using this formula, we can for instance use a computer algebra system to deduce $\Dnka nka$ for small values of $k$, see Table \ref{tab:Dnka_small_k}. Note that even though the expression for $\Dnka n3a$ involves a division by $3$, its evaluation at specific values for $(p,q,r)$ will always yield integers. Indeed, either $p-q\equiv 0\bmod 3$, or $(p-q)^2\equiv 1\bmod 3$, in which case $2(p-q)^2+7\equiv 0\bmod 3$.

    \begin{table}
    	\centering
    	\begin{tabular}{|c|c|}
    		\hline
    		$k$ & $\Dnka nka$\\ \hline
    		$0$&$1$\\ \hline
            $1$&$2(p-q)$\\ \hline
            $2$&$2(p-q)^2-3(p+q)+r$\\ \hline
            $3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\ \hline
    	\end{tabular}
    	\caption{Values of $\Dnka{n}{k}{a}$ for small $k$}\label{tab:Dnka_small_k}
    \end{table}
\end{remark}

@@

One can also prove the following:

\begin{Prop}
    For a fixed integer $k\geq 1$ and sufficiently large $n\geq b(k)$, it holds that:
    \[
        \max_{a\in\F_2^n}|\Dnka nka|=|\Dnka nk{0_n}|=\left(-\frac12\right)^k\sum_{i=\lceil k/2\rceil}^{n/2}(-4)^i\binom{n/2}{i}\binom{i}{k-i}.
    \]
\end{Prop}

\begin{remark}
    In general, it also appears that the vector $a\in\F_2^n$ for which $|\Dnka nka|$ is maximal always satisfies $r(a)=0$.
\end{remark}

Also, using the Cauchy estimate on holomorphic functions, we can prove:

\begin{Prop}
    For any real number $R>0$, we have the following bound:
    \[
        |\Dnka nka|\leq\frac{(M_R)^{n/2}}{R^k},
    \]
    where $B_R$ is the maximum of $\left|z^2-2z-1\right|$ on the complex disk $|z|=R$. Explicitly, $M_R$ can be expressed as follows:
    \[
        M_R=
        \begin{cases}
            -R^2+2R+1&\text{if $R\leq\sqrt 2-1$}\\
            \sqrt 2\left(R^2+1\right)&\text{if $\sqrt 2-1\leq R\leq\sqrt 2+1$}\\
            R^2+2R-1&\text{if $R\geq\sqrt 2+1$}\\
        \end{cases}.
    \]
\end{Prop}

\begin{remark}
Here are some interesting choices for $R$:
\begin{itemize}
    \item Choosing $R=1/\sqrt 2$ yields that $|\Dnka nka|\leq\left(3/\sqrt 2\right)^{n/2}\cdot \sqrt 2^k$.
    \item Choosing $R=1/2$ gives $|\Dnka nka|\leq (5\sqrt 2/4)^{n/2}\cdot 2^k$.
\end{itemize}
\end{remark}
